Per captia consumption

### 2021-06-15 NOBA_cod_files/README.Rmd

### Plot SAM fits
```{r, fig.height = 2, sam_fit}
par(mfrow = c(1, 1))
ssbplot(sam_fit)
fbarplot(sam_fit)
recplot(sam_fit)
catchplot(sam_fit)
```

@@

### Compare SAM outputs and SS outputs
```{r, warning = FALSE, message = FALSE, fig.height = 2, sam_ss_comparison}
sam_output <- data.frame(
  "Year" = c(sam_dat$years),
  "SSB" = exp(sam_fit$sdrep$value[names(sam_fit$sdrep$value) %in% "logssb"]),
  "Recruits" = exp(sam_fit$sdrep$value[names(sam_fit$sdrep$value) %in% "logR"]),
  "F" = exp(sam_fit$sdrep$value[names(sam_fit$sdrep$value) %in% "logfbar"]),
  "Catch" = c(exp(sam_fit$sdrep$value[names(sam_fit$sdrep$value) %in% "logCatch"]), NA)
)

@@

### Userful resources
  - [SAM GitHub repository](https://github.com/fishfollower/SAM)
	- Aldrin et al., 2020: [The specification of the data model part in the SAM model matters](https://www.sciencedirect.com/science/article/pii/S0165783620301028#bib0020)
	- Nielsen and Berg, 2014: [Estimation of time-varying selectivity in stock assessments using state-space models](https://www.sciencedirect.com/science/article/abs/pii/S0165783614000228?via%3Dihub)
	- Berg and Nielsen, 2016: [Accounting for correlated observations in an age-based state-space stock assessment model](https://academic.oup.com/icesjms/article/73/7/1788/2458744)
	- [ICES Report of the Arctic Fisheries Working Group (AFWG)](https://www.ices.dk/sites/pub/Publication%20Reports/Expert%20Group%20Report/acom/2018/AFWG/00-AFWG%202018%20Report.pdf)

>>>>

### Plot SAM fits
```{r, fig.height = 6, sam_fit}
par(mfrow = c(1, 1))
ssbplot(sam_fit)
fbarplot(sam_fit)
recplot(sam_fit)
catchplot(sam_fit)
```

@@

### Compare SAM outputs and SS outputs
```{r, warning = FALSE, message = FALSE, fig.height = 6, sam_ss_comparison}
sam_output <- data.frame(
  "Year" = c(sam_dat$years),
  "SSB" = exp(sam_fit$sdrep$value[names(sam_fit$sdrep$value) %in% "logssb"]),
  "Recruits" = exp(sam_fit$sdrep$value[names(sam_fit$sdrep$value) %in% "logR"]),
  "F" = exp(sam_fit$sdrep$value[names(sam_fit$sdrep$value) %in% "logfbar"]),
  "Catch" = c(exp(sam_fit$sdrep$value[names(sam_fit$sdrep$value) %in% "logCatch"]), NA)
)

@@

### Resources
  - [SAM GitHub repository](https://github.com/fishfollower/SAM)
	- Aldrin et al., 2020: [The specification of the data model part in the SAM model matters](https://www.sciencedirect.com/science/article/pii/S0165783620301028#bib0020)
	- Nielsen and Berg, 2014: [Estimation of time-varying selectivity in stock assessments using state-space models](https://www.sciencedirect.com/science/article/abs/pii/S0165783614000228?via%3Dihub)
	- Berg and Nielsen, 2016: [Accounting for correlated observations in an age-based state-space stock assessment model](https://academic.oup.com/icesjms/article/73/7/1788/2458744)
	- [ICES Report of the Arctic Fisheries Working Group (AFWG)](https://www.ices.dk/sites/pub/Publication%20Reports/Expert%20Group%20Report/acom/2018/AFWG/00-AFWG%202018%20Report.pdf)
